Joint Training of Classification and Similarity Models for \\ Intention Detection in Task-specific Chatbot

### 2020-09-10 chatbot_classification/aaai_2021/experiments.tex
modified:   experiments.tex

\subsection{Result Analysis}
We  report  the F1 score \footnote{In the multi-class and multi-label case, this
is  the  average  of  the F1 score of each class with weighting depending on the
numbers  in  each class.}. as the main evaluation measure for all experiments in
Table \ref{tbe:table2}.

>>>>

\subsection{Result Analysis}
We  report  the F1 score \footnote{In the multi-class and multi-label case, this
is  the  average  of  the F1 score of each class with weighting depending on the
numbers  in  each class.} as the main evaluation measure for all experiments in
Table \ref{tbe:table2}.
